Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-02-02 paper/main.tex
Added discussion of CPU Parallelism

@@

\section{CPU Implementation}
% With a reshuffling of the order of operations and a change of the termination
% condition, the inner loop takes the form of two matrix-vector multiplications
% and a sequence of vector-vector operations.
\subsection{CPU Hardware Parallelism}
High-level discussion of CPU parallelism, i.e.
thread-level, vector-level, cache size, cache locality
\subsection{Tuning the GEMV operation}
When matrix-vector operations are called sequentially on the same data,
the operation can be blocked so that each thread operates on the same block of data for each operation.

For Single threaded MKL sgemv, Code took          0.0335823 msec per instance to run!

For Automatic multi-threaded MKL sgemv, Code took 0.008179 msec per instance to run!

For Manually multi-threaded MKL sgemv, Code took  0.0061276 msec per instance to run!

\subsection{Tuning the Soft-Thresholding Operator}
...Make sure there are no branches

...Make sure there are no function calls

...Make sure the loop gets automatically vectorized

...Block the computation into work for different cpu cores

>>>>

% With a reshuffling of the order of operations and a change of the termination
% condition, the inner loop takes the form of two matrix-vector multiplications
% and a sequence of vector-vector operations.

@@

\section{CPU Implementation}
\subsection{CPU Hardware Parallelism}
The baseline architecture for our experiments is 
a typical high end workstation with two quad-core Intel Nehalem E5530 processors clocked at 2.4 GHz.
Each processor has its own memory interface, and is directly connected to half of the
RAM installed in the machine.  The amount of RAM installed exceeds the amount used
by the algorithms, and is not an important performance consideration.

Each core has a 32 KB L1 data cache and a 256 KB L2 cache. With Hyperthreading enabled, each core can
support two threads simultaneously.  For floating point math, each core also has a vector unit capable of
performing the same arithmetic operation on 4 single precision floating point values simultaneously.
\footnote{The core also has scalar floating point units, but some compilers, notably gcc, generate
code that uses the vector units exclusively for floating point math.}

There are thus two important levels of parallelism that need to be exploited to use
a modern cpu efficiently: core-level parallelism and vector-level parallelism.
For the implementations discussed here, we will primarily use the OpenMP programming model 
to express core-level parallelism.  Depending on the section of the code, we will achieve vector-level parallelism 
implicitly through either the auto-vectorization features of Intel's icc compiler, 
or through the use of a highly optimized BLAS library (Intel's MKL).

Each processor has 8MB of L3 cache that is shared by all 4 cores.
Overall, this means the algorithm has approximately 16MB of on-chip cache available.  
For the low resolution images used in sparse representation based face recognition,
this is enough cache to hold over 800 image-sized variables, meaning that for small data sets
it is possible to run completely using on-chip cache.

%\subsection{Tuning the GEMV operation}
%When matrix-vector operations are called sequentially on the same data,
%the operation can be blocked so that each thread operates on the same block of data for each operation.
%For Single threaded MKL sgemv, Code took          0.0335823 msec per instance to run!
%For Automatic multi-threaded MKL sgemv, Code took 0.008179 msec per instance to run!
%For Manually multi-threaded MKL sgemv, Code took  0.0061276 msec per instance to run!

%\subsection{Tuning the Soft-Thresholding Operator}
%...Make sure there are no branches
%...Make sure there are no function calls
%...Make sure the loop gets automatically vectorized
%...Block the computation into work for different cpu cores
